---
title: "simpleRegress"
author: "Deniss Gonzalez Ramirez"
date: "Fall 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Introduction

We are attempting to find a variable that is a better predictor of the length of the bear than its neck size.


## Simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
```


## Model LENGTH ~ NECK    

```{r}
simp <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simp)
summary.lm(simp)
```

Neck as a variable determining a bears length had an adjusted R-squared score of 0.7476.  The scatter plot shows that as the neck size goes up, length does as well, this neck size is a good predictor to determine length. 


## Prediction of the length of a bear who has a neck of 17, 22 and 26


```{r}
new <- data.frame(NECK=c(17,22,26))
predict(simp,new)
predict(simp,new,se.fit=TRUE,interval = "prediction")
```


## Numerical Summary

```{r}
cor(bears$LENGTH,bears$NECK)
```

The correlation coefficient is a measure of the linear relationship between the two variables.


## Model LENGTH~CHEST

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

Chest as the variable for determining a bear's length had an adjusted R-squared score of 0.7869.

The scatter plot shows that as the neck size goes up, length does as well and the neck size is a good predictor in terms of determining the length of a bear.

## Numerical Summary

```{r}
cor(bears$LENGTH,bears$CHEST)
```

The correlation coefficient is a measure of the linear relationship between the two variables.

## Conclusion

Chest had an adjusted R-squared value of 0.7869
Neck had an adjusted R-squared value of 0.7476
We can conclude that Chest is a better predictor of length than Neck is. We know this because the adjusted R-squared test of the fit for CHEST was larger than the adjusted R-squared of the fit for NECK. The adjusted R-squared 